Hyper-linked Communications: WebRTC enabled asynchronous collaboration

### 2015-06-02 tese/project.tex
started conclusions

\section{Conclusions}\label{concl} % English

>>>>

\section{Conclusions}\label{concl} % English
  The development of WebRTC by the World Wide Web Consortium (W3C) allows web browser-to-browser audio, video and data communication. WebRTC is enabling new usage scenarios for communication and collaboration applications. However, the nature of such scenarios lead to significant challenges, such as the need to record interactive audio and video streams.

  This project proposes a solution that uses WebRTC for creating an application that provides audio, data, text and data real-time communications. Theses communications will be enriched using hypermedia concepts, the possibility to record and playback interactive content and the integration of collaborative tools.
